%
% The MIT License (MIT)
%
% Copyright (c) 2017 Paul Batty
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
% THE SOFTWARE.
%

\section{Cost benefits}
\label{sec:costbenefits}

After looking at the entire pipeline this next section is dedicated to who should use such a system, as in when does it become beneficial to set-up all the overhead required to actually bring benefits.

\subsection{Benefits}

There have been a few benefits mentioned throughout the paper the main one being the quick feedback loop that can be provided however there are a lot more that have not yet been mentioned.
\\\\
Firstly, as the pipeline is automated the project can be tested on all the different target systems with ease. This in turn will reduce the number of problems that can or might occur when deploying to a new or existing system. By doing so will allow developers to have a higher level of confidence in that the software will work on any system.
\\\\
Secondly, it keeps the number of bugs low and the code quality to a set standard,  as the entire system is automated the tests that are run ensure that there is a level of confidence in that there are no major bugs in the system. If there are, that they can be fixed quickly and put out to the users. The code quality while not a substitute for code reviews can still be automatically checked, making sure the style of the code is consistence. 
\\\\
Thirdly, with the quick feedback loop, there are benefits for everyone not only developers working on the software. As the automation tool is keeping logs and can send notifications to everyone who wants to keep in the know or gather information about the software can do so easily. Not just the information about the process but easy access to the binaries / packages to make additional deployments or set-ups.
\\\\
Overall projects with continuous deployment or continuous integration end up with a higher base level of quality and bugs than those without, although it does not fix or prevent bugs from being created it allows developers and managers to see what does and does not and what is needed to make the system work, while preventing old bugs from being introduced to the system. On top of this the feedback is invaluable to everyone involved in the software pipeline, from developers to managers, creating an environment where everyone is more confident in the product as there are logs and process data available to back the claims ups.


\subsection{Cost}

While the benefits are great there are some costs that come with implementing continuous integration, delivery or other forms of these systems.
\\\\
Firstly, the initial upfront costs are expensive, getting the severs or to rent a system from a cloud service. This is both time and money spent getting the systems set-up and running in a way that will suit the software package. 
\\\\
In the same vain if there are no tests the cost of writing the tests in the first place is a slow and steady process that will not happen overnight, as they have to be created and integrated into the new system. In addition to this the current tools may have to be adapted the new system, for example changing the VCS from TFS to GIT to provide better services. There are a lot of up font costs involved if the system is not simple or is not designed to allow this type of operation from the start, which excludes the trouble of specialised hardware and having to emulate them. 
\\\\
Secondly, when the system is up and running there is a maintenance cost attached to the tests, if the software updates and changes a core part of the system, so do the tests. There is also the matter of flaky tests that may or may not pass.
\\\\
The idea of workflow is an important one as there maybe need to change the way developers commit, from every now and then to committing more frequently for smaller changes. These types of costs will heavily depend on the current situation of the project for example a project that already practises test driven development will have a lot of tests already written and so will find it easier to move over to continuous deployment as all they have to do is hook up the tests whereas a project with no tests will have to start from scratch. 
\\\\
Excluding the technical costs and focusing on the personal, users will have to be trained to both understand how, why and what continuous deployment is and how it can benefit them, else they will have a tenancy to shy away from it. This will also require training on the new workflow or hiring addition people to come in and maintain the systems also known as devops as mentioned towards the start of this paper. The main issue is while developers can run this system themselves, continuous delivery can effect everyone involved in the process, this not only means getting developers training but managerial, QA and sales. 

\subsection{Who}

From the lists above it should be clear who can benefit from creating a system, the solo developer or the massive multilevel corporation.
\\\\
A paper by \cite{ossuse} looked at the use of continuous integration in open source software finding that by using it, developers have a highier confidence in the software and release twice as often then those who do not. A similar study by \cite{ossprod} showed that there is an increase in productivity and no drop in code quality or otherwise.
\\\\
While there are plenty of cases where it can and should be used, it is easier to list off the places where continuous deployment may instead be worse. This comes in from three factors firstly the team size, secondly the project size and finally the project type.
\\\\
Firstly, team size plays a role as the system is a type of managerial tool, as a solo developer there is still reason to use continuous deployment to manage and keep tabs on the status of the project. The system however does come into its own when more people get involved as everyone can be kept up to date on the ongoings of the project. If for instance working in an open source project at the start it may only be a solo developer but when others start contributing the project, the workflow will easily be able to scale up to and support the larger number of developers.
\\\\
Secondly the project size, a small 50 line script compared to a million plus of lines in a web application come nowhere near close to comparing. There is almost going to be more set up and code in the automation tool for the first project then the second. Not only that but it is very a inefficient use of time and effort as the tools are not designed to work at this small of a scale as found by \cite{smallci}.
\\\\
Thirdly, keeping in mind the project size, a small automation script is hardly worth the trouble, similarly, if that script however is used by everyone in the project for everyone in the team, a small bug fix  might tip the balance in favour of moving towards continuous delivery to make sure that everyone is using the latest version. 
\\\\
With these ideas in mind one does not have to go from nothing to continuous delivery, there are various middle grounds that might be better used or on the route to implementing continuous delivery into the project. These include automating the build, test automation and continuous integration. In addition to this, when deciding what type to go for will heavily depend on the current situation of the project, the project type and team size.

\subsection{Cost benefits final thoughts}

Overall while continuous deployment and its variations bring many benefits the initial uphill climb and ongoing maintenance may not be for every project. Although it would always be a helping hand increasing the base level of confidence in the project.
